Model LF

### 2022-09-22 Estimation.Rmd
commit

@@

@@

test_dummy= d_2009q1 + d_2009q2 
reg_wage_ds_start=dynlm(TSDELTALOG(wage_ds) ~ 1+ L(TSDELTA(wage_ds), 1:4) + L(TSDELTA(ur), 0:4)+ L(TSDELTALOG(prod_ds), 0:4)+  L(log(wage_ds_t_new), 1)  + log(TSLAG(wage_ds,1))  + log(TSLAG(prod_ds,1)) +  test_dummy)

@@

 wage_ds_vars_1 <- str_c("L(TSDELTA(wage_ds), 1:4)", c(1,2,3,4))
 ur_ds_vars_1 <- str_c("L(TSDELTA(ur), 0:4)", c(0,2,3,4))
 prodk_ds_vars_1 <- str_c("L(TSDELTALOG(prod_ds), 0:4)", c(1,2))

@@

vars_out_1 <- c( wage_ds_vars_1,ur_ds_vars_1,prodk_ds_vars_1 )
vars_out_1

@@

```{r}
reg_wage_ds=dynlm(TSDELTALOG(wage_ds) ~ 0 + L(TSDELTA(ur), 1)+ L(TSDELTALOG(prod_ds), c(0,3,4))+  L(log(wage_ds_t_new), 1)  + log(TSLAG(wage_ds,1))  + log(TSLAG(prod_ds,1)) +  test_dummy)

>>>>

## Change to wage equation

mean((TSLAG(wage_ds,1)-obs_dp_q)/obs_dp_q)
wage_gab_wanted= obs_dp_q*0.6870502

@@

**Test med forskellige løn scenarier**

@@

mean_dp_growth= TSDELTA(mean_dp_regul,4)/TSLAG(mean_dp_regul,4)

obs_dp_growth= TSDELTA(obs_dp_q,4)/TSLAG(obs_dp_q,4)

wage_ds_growth= TSDELTA(wage_ds,4)/TSLAG(wage_ds,4)

dummy_test= ifelse(mean_dp_growth > wage_ds_growth, 1,0)

dummy_test1= ifelse(obs_dp_growth > wage_ds_growth, 1,0)

wage_gap= TSLAG(wage_ds,1)- mean_dp_regul

wage_ratio= TSLAG(wage_ds,1)/ mean_dp_regul

```{r}
options(scipen = 999)

test_dummy= d_2009q1 + d_2009q2 
reg_wage_ds_start=dynlm(TSDELTALOG(wage_ds) ~ 1+ L(TSDELTA(wage_ds), 1:4) + L(TSDELTA(ur), 0:4)+ L(TSDELTALOG(prod_ds), 0:4) + L(wage_ratio, 0)+  L(log(wage_ds_t), 1)  + log(TSLAG(wage_ds,1))  + log(TSLAG(prod_ds,1)) + test_dummy)

@@

 wage_ds_vars_1 <- str_c("L(TSDELTA(wage_ds), 1:4)", c(1,3,4))
 ur_ds_vars_1 <- str_c("L(TSDELTA(ur), 0:4)", c(0,2,3,4))
 prodk_ds_vars_1 <- str_c("L(TSDELTALOG(prod_ds), 0:4)", c(1,2,3,4))
 mean_dp_regul_vars_1 <- str_c("L(TSDELTALOG(mean_dp_regul), 0:4)", c(0,1,3,4))

@@

vars_out_1 <- c( mean_dp_regul_vars_1, wage_ds_vars_1,ur_ds_vars_1,prodk_ds_vars_1 )
vars_out_1

@@

```{r}
reg_wage_ds=dynlm(TSDELTALOG(wage_ds) ~ 0 + L(TSDELTA(ur), 1)+ L(TSDELTALOG(prod_ds), 0)+ L(TSDELTALOG(mean_dp_regul), 2)+  L(log(wage_ds_t), 1)  + log(TSLAG(wage_ds,1))  + log(TSLAG(prod_ds,1)) + (log(TSLAG(mean_dp_regul,1)):dummy_test) + test_dummy )
